HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

\paragraph{Technical Differences}

+ allows for multi-word and even non-contiguous elements

+ allows to indicate the quality of the predicates ("Actions")

>>>>

\paragraph{Annotation of Predicates}

HUME allows to annotate multi-word and even
non-contiguous elements as a single unit. HMEANT, on the other hand, always
required exactly one word to be annotated as the predicate (``Action''), which
is often linguistically inadequate.

Another problem with HMEANT identified by \parcite{bojar:wu:ssst:2012} was the

inability to indicate that the predicate is somewhat mistranslated (e.g.
accidentally negated or in a slightly wrong tense). HMEANT
annotation allows either to mark the source and reference frames as matching
(which implies that the corresponding predicates are correct translations of each
other), or as non-matching (which leads to a zero score for the whole frame) but
nothing in between. In HUME, the verb is still present as a sub-unit of the
frame and has the traffic-lights annotation.
